Calculate FD

### 2020-07-25 analysis/calc_fd.Rmd
Clean up reading back in data and creating fd_table.

  setwd(here::here())
  print(filter_plot)
  return(fd_out)
}

@@

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot)) %>% #remove unlabeled plots 
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  group_by(plot_id) %>%
  filter(n_distinct(year) > 4) %>% 
  ungroup()# %>%
  #filter(!study_id %in% c(195, 360), #exclude because they break
         #!study_id %in% c(217, 327)) #exclude to get the file size smaller

@@

library(furrr)
future::plan(multiprocess)
system.time(fd <- future_map_dfr(plots, get_fd_safe, data = data))
```

@@

get_parallel_FD <- function(data, group_num){
  group_plots <- plot_sizes %>% filter(group == group_num)
  group_data <- data %>% filter(plot_id %in% group_plots$plot_id)

  future::plan(multiprocess)
  fd <- future_map_dfr(group_plots$plot_id, get_fd_safe, data = group_data)

  print(group_num)
  return(FD)
}

fd <- map_dfr(1:num_groups, get_parallel_FD, data = data)
```

@@

remain <- biotime_traits %>%
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  filter(!is.na(plot), !study_id %in% c(195, 360),
         !study_id %in% c(217, 327), #exclude to get the file size smaller
         !study_id %in% c(59, 166, 337), #NA's in the distance matrix
         study_id != 169,  #Zero distance error
         !study_id %in% c(372,374), #Qhull error code 4
         study_id != 333) %>% #species distance matrix not Euclidean after 'sqrt' correction
  filter(study_id != 56 | plot != 24) %>% #NA's in the distance matrix
  anti_join(fd_data, by = c("year", "study_id", "plot")) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup()

plots <- remain %>%
  pull(plot_id) %>%
  unique()

library(furrr)
future::plan(multiprocess)
system.time(fd <- future_map_dfr(plots, get_fd_safe, data = data))
```

@@

Format tables
```{r}
fd_table <- fd_data %>% 
  select(year, study_id, plot, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ)

>>>>

  setwd(here::here())
  print(filter_plot)
  #return(fd_out)
}

@@

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot)) %>% #remove unlabeled plots 
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  group_by(plot_id) %>%
  filter(n_distinct(year) > 4) %>% 
  ungroup() #%>%
  #filter(#!study_id %in% c(195, 360), #exclude because they break
         #!study_id %in% c(217, 327, 195)) #exclude to get the file size smaller

@@

#system.time(fd <- future_map(plots[1:3], get_fd_safe, obs_data = data))
```

@@

get_parallel_FD <- function(df, group_num){
  group_plots <- plot_sizes %>% filter(group == group_num)
  group_data <- df %>% filter(plot_id %in% group_plots$plot_id)

  future::plan("multiprocess", workers = 4)
  fd <- future_map(group_plots$plot_id, get_fd_safe, obs_data = group_data) %>%
    rbind()

  print(group_num)
  return(fd)
}

#fd <- map(1:num_groups, get_parallel_FD, df = data)
```

@@

remain <- data %>%
  filter(!plot_id %in% fd_data$plot_id, !plot_id %in% c(1661, 196456, 3721, 3601))

plot_sizes <- remain %>%
  count(plot_id) %>%
  arrange(desc(n)) %>%
  mutate(group = rep_len(1:num_groups, dim(.)[1]))

#fd <- map(1:num_groups, get_parallel_FD, df = remain)

system.time(fd <- map(plot_sizes$plot_id, get_fd_safe, obs_data = data))
```

@@

Format tables
```{r}
fd_table <- fd_data %>% 
  select(year, plot_id, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ) %>%
  left_join(biotime_traits %>% 
              select(plot_id, study_id, plot) %>% 
              mutate(plot_id = as.numeric(plot_id)) %>%
                       distinct())
